Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-18 lqg-strings.tex
used subequation environment on places where there was multiple eqns

When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get two-indices \textquotedblleft Virasoro modes"
\begin{align}
	L_{n , p} := \alpha ^{\mu} _{n} \alpha ^{\nu} _{p} \eta _{\mu \nu}                                                         & = 0 , \ \forall \ n , p \in \mathbb{Z} , \label{eqn:"virasoro"-modes-1} \\
	\widetilde{L}_{n , p} := \alpha ^{\mu} _{n} (\alpha ^{\nu} _{p})^{*} \eta _{\mu \nu}                                       & = 0 , \ n \neq p , \label{eqn:"virasoro"-modes-2}                       \\
	\sum _{n} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) & = 0 \label{eqn:"virasoro"-modes-sum} .
\end{align}
Constraint \eqref{eqn:"virasoro"-modes-2} implies that we only have $D$ independent expansion modes for each field $X^{\mu}$, which for consistency as we will see later means $\alpha ^{\mu} _{- p} = \alpha ^{\mu} _{p} , \ p \leq d = D - 1$ and $\alpha ^{\mu} _{n} = 0 , \ \forall \ |n| > d$, so we have a truncated solution. This is not surprising, since because space-time is discrete we expect wavelengths smaller than the granular structure to be ruled out.

@@

We start by calculating the canonical momentum density conjugate to the fields $X^{\mu} (x)$, $\Pi ^{\nu} (x)$, given by
\begin{multline} \label{eqn:canonical-momentum-density}
	\Pi ^{\nu} (x) = F^{-} \frac{i}{8 \pi \alpha '} \sum _{n} \bigg( \alpha ^{\nu} _{n} \e ^{i (E_{n} \tau - n \sigma)} - \\
	- (\alpha ^{\nu} _{n})^{*} \e ^{- i (E_{n} \tau - n \sigma)} \bigg)
\end{multline}
where
\begin{multline} \label{eqn:F-minus-full-sum}
	F^{-} = 1 - \frac{k \Delta}{2 \e ^{2 \phi (x)}} = \\
	= \sum _{l} \left( A_{l} \e ^{i (E_{l} \tau + l \sigma)} + (A_{l})^{*} \e ^{- i (E_{l} \tau + l \sigma)} \right) ,
\end{multline}
and then proceed to use the equal-time Poisson bracket relation at $\tau = 0$
\begin{equation} \label{eqn:canonical-bracket-relation}
	\left\{ X^{\mu} (0 , \sigma) , \Pi ^{\nu} (0 , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
\end{equation}
to calculate the bracket relations between the expansion modes $\alpha ^{\mu} _{n}$ and $(\alpha ^{\nu} _{p})^{*}$. After using the freedom we still have in choosing the expansion modes of $F^{-}$ to gauge fix it to satisfy $\mathfrak{Re} (A_{0}) = - 2 \alpha '$ and realizing that $\alpha ^{\mu} _{- n} = \alpha ^{\mu} _{n}$, we get the desired
\begin{equation} \label{eqn:expansion-modes-bracket-0}
	\left\{ \alpha ^{\mu} _{n} , \alpha ^{\nu} _{p} \right\} = 0 = \left\{ (\alpha ^{\mu} _{n})^{*} , (\alpha ^{\nu} _{p})^{*} \right\}
\end{equation}
\begin{equation} \label{eqn:expansion-modes-bracket-1}
	\left\{ \alpha ^{\mu} _{n} , (\alpha ^{\nu} _{p})^{*} \right\} = - i E_{n} \delta _{|n| , |p|} \eta ^{\mu \nu} ,
\end{equation}
from which we can normalize the expansion modes to get harmonic oscillator modes and bracket relations
\begin{align}
	a^{\mu} _{n}       & := \frac{1}{\sqrt{E_{n}}} \alpha ^{\mu} _{n} \label{eqn:normalized-oscillator-modes}         \\
	(a^{\mu} _{n})^{*} & := \frac{1}{\sqrt{E_{n}}} (\alpha ^{\mu} _{n})^{*} \label{eqn:normalized-oscillator-modes-*}
\end{align}
\begin{equation} \label{eqn:harmonic-bracket-relations}
	\left\{ a^{\mu} _{n} , (a^{\nu} _{p})^{*} \right\} = - i \delta _{|m| , |l|} \eta ^{\mu \nu} .
\end{equation}
The bracket relations for $\alpha ^{\mu} _{0}$ can be used to get the expected bracket relations between $x^{\mu}$ and $p^{\nu}$
\begin{align}
	\left\{ x^{\mu} , x^{\nu} \right\} & = 0 = \left\{ p^{\mu} , p^{\nu} \right\} \label{eqn:x-x-p-p-brackets} \\
	\left\{ x^{\mu} , p^{\nu} \right\} & = \eta ^{\mu \nu} . \label{eqn:x-p-bracket-relations}
\end{align}

@@

Having the bracket relations between the vibrational modes of the string, we can now calculate the constraint algebra, which we shall refer to as the Virasoro-Klein-Gordon Algebra. For simplicity, since $E_{n} = \sqrt{n^2 + \mu ^2} > 0$, we shall work with the normalized harmonic oscillator modes $a^{\mu} _{n}$ instead of the expansion modes $\alpha ^{\mu} _{n}$. The algebra is given by
\begin{equation} \label{eqn:L-brackets-0}
	\left\{ L_{n , m} , L_{k , p} \right\} = 0
\end{equation}
\begin{equation} \label{eqn:L-brackets-1}
	\left\{ L_{n , m} , \widetilde{L}_{k , p} \right\} = - i \left( L_{m , k} \delta _{|n| , |p|} + L_{n , k} \delta _{|m| , |p|} \right)
\end{equation}
\begin{equation} \label{eqn:L-brackets-2}
	\left\{ \widetilde{L}_{n , m} , \widetilde{L}_{k , p} \right\} = - i \left( \widetilde{L}_{k , m} \delta _{|n| , |p|} - \widetilde{L}_{n , p} \delta _{|m| , |k|} \right) .
\end{equation}

@@

We now seek to quantize the Klein-Gordon string by means of covariant canonical quantization, in a manner much similar to those found in (\cite{Tong2009Lectures},\cite{Green2012Superstring}). The string coordinates $X^{\mu}$ and it's conjugate momentum $\Pi ^{\nu}$ are turned into operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$, with the Poisson brackets $\{ . , . \}$ being replaced by commutators $\{ . , . \} \rightarrow - i [ . , . ]$:
\begin{align}
	\left[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \right] & = i \delta (\sigma - \sigma ') \eta ^{\mu \nu} \label{eqn:X-P-commutator}                                              \\
	\left[ \Hat{X}^{\mu} , \Hat{X}^{\nu} \right]                                     & = 0 = \left[ \Hat{\Pi}^{\mu} , \Hat{\Pi}^{\nu} \right] \label{eqn:X-X-P-P-commutators}                                 \\
	\left[ \Hat{a}^{\mu} _{n} , \Hat{a}^{\nu} _{p} \right]                           & = 0 = \left[ (\Hat{a}^{\mu} _{n})^{\dagger} , (\Hat{a}^{\nu} _{p})^{\dagger} \right] \label{eqn:a-a-a*-a*-commutators} \\
	\left[ \Hat{a}^{\mu} _{n} , (\Hat{a}^{\nu} _{p})^{\dagger} \right]               & = \delta _{|n| , |p|} \eta ^{\mu \nu} \label{eqn:a-a*-commutator}                                                      \\
	\left[ \Hat{x}^{\mu} , \Hat{x}^{\nu} \right]                                     & = 0 = \left[ \Hat{p}^{\mu} , \Hat{p}^{\nu} \right] \label{eqn:x-x-p-p-commutators}                                     \\
	\left[ \Hat{x}^{\mu} , \Hat{p}^{\nu} \right]                                     & = i \eta ^{\mu \nu} \label{eqn:x-p-commutator}
\end{align}

As usual, we define the vacuum state of the string to obey
\begin{equation} \label{eqn:annihilation-vacuum}
	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 .
\end{equation}
For $p = 0$ we have center of mass position and momentum, so the vacuum has extra structure obeying
\begin{align}
	\Hat{x}^{\mu} \ket{0 ; x} & = x^{\mu} \ket{0 ; x} \label{eqn:x-vacuum-x}                       \\
	\Hat{p}_{\mu} \ket{0 ; 0} & = - i \frac{\del}{\del x^{\mu}} \ket{0 ; x} \label{eqn:p-vacuum-x}
\end{align}
in position representation and
\begin{align}
	\Hat{x}^{\mu} \ket{0 ; p} & = - i \frac{\del}{\del p_{\mu}} \ket{0 ; p} \label{eqn:x-vacuum-p} \\
	\Hat{p}_{\mu} \ket{0 ; p} & = p_{\mu} \ket{0 ; p} \label{eqn:p-vacuum-p}
\end{align}
in momentum representation.

@@

When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
\begin{equation} \label{eqn:L-constraint-quantum-1}
	\bra{\phi} \Hat{L}_{p , k} \ket{\psi} = 0 \, \,
\end{equation}
\begin{equation} \label{eqn:L-constraint-quantum-2}
	\bra{\phi} \Hat{\widetilde{L}}_{p , k} \ket{\psi} = 0 .
\end{equation}
$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators. As for $\widetilde{L}_{p , k}$, we have an ambiguity for $p = k \neq 0$, so we pick normal ordering with the annihilation operator to the right
\begin{equation} \label{eqn:L-normal-ordering}
	\Hat{\widetilde{L}}_{p , p} = (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu} .
\end{equation}
This ambiguity manifests in the imposition of the constraint as
\begin{equation} \label{eqn:shifted-L-constraint}
	\bra{\phi} \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \Hat{\widetilde{L}}_{n , n} \right) - a \right) \ket{\psi} = 0 ,
\end{equation}
for some constant $a$. Classically, we had eq (\ref{eqn:string-rest-mass-classical-1}) for the string rest mass, from which we can now see that the string mass spectrum will get shifted by
\begin{multline} \label{eqn:shifted-mass-spectrum}
	\Hat{M}^2 = \frac{8}{\alpha '} \Bigg( \frac{2 \mu ^2}{\alpha '} \Hat{x}^{\mu} \Hat{x}_{\mu} - \\
	- \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} (\Hat{a}^{\mu} _{n})^{\dagger} \Hat{a}^{\nu} _{n} \eta _{\mu \nu} \right) - a \right) \Bigg) .
\end{multline}
This constant can be calculated by imposing normal-ordering on the summed constraint since $n \in (- d , d)$ is finite, and the result is
\begin{multline}
	a = - D \sum _{n \neq 0} \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} = \\
	= - D \sum _{n > 0} \left( 1 + \frac{n^2}{E_{n} ^2} \right) E_{n} .
\end{multline}

The commutation relations between the constraints are inherited by the Poisson brackets
\begin{align}
	\left[ \Hat{L}_{n , m} , \Hat{L}_{k , p} \right]                         & = 0 \label{eqn:L-commutator-0}                                                                                                   \\
	\left[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right]             & = \Hat{L}_{m , k} \delta _{|n| , |p|} + \Hat{L}_{n , k} \delta _{|m| , |p|} \label{eqn:L-commutator-1}                           \\
	\left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] & = \Hat{\widetilde{L}}_{k , m} \delta _{|n| , |p|} - \Hat{\widetilde{L}}_{n , p} \delta _{|m| , |k|} \label{eqn:L-commutator-2} .
\end{align}
The commutator (\ref{eqn:L-commutator-1}) ends up with only annihilation operators in the R.H.S, so it has no ordering ambiguities, meanwhile the commutator (\ref{eqn:L-commutator-2}) have ordering ambiguities for $|m| = |k|$ and/or $|n| = |p|$, so we add the anomalous terms
\begin{multline} \label{eqn:L-commutator-anomalous-initial}
	\left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] = \Hat{\widetilde{L}}_{k , m} \delta _{|n| , |p|} - \Hat{\widetilde{L}}_{n , p} \delta _{|m| , |k|} + \\
	+ C_{n} \delta _{|n| , |p|} + D_{k} \delta _{|m| , |k|} .
\end{multline}
Clearly, $C_{0} = D_{0} = 0$, since when all indices are $0$ we have only the position and momentum operators, and thus the commutator should vanish identically. Also, because of the symmetry in the indices we have that $C_{- n} = C_{n}$ and $D_{- k} = D_{k}$. Using the Jacobi identity
\begin{multline} \label{eqn:L-Jacobi-identity}
	\left[ \Hat{\widetilde{L}}_{n , m} , \left[ \Hat{\widetilde{L}}_{k , p} , \Hat{\widetilde{L}}_{r , s} \right] \right] + \\
	+ \left[ \Hat{\widetilde{L}}_{r , s} , \left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] \right] + \\
	+ \left[ \Hat{\widetilde{L}}_{k , p} , \left[ \Hat{\widetilde{L}}_{r , s} , \Hat{\widetilde{L}}_{n , m} \right] \right] = 0
\end{multline}
we get the difference equation
\begin{equation} \label{eqn:F-difference-eqn}
	F_{n + 1} + F_{n} + F_{1} = 0
\end{equation}
for the sum of both sequences $F_{n} = C_{n} + D_{n}$. This difference equation has solution
\begin{equation} \label{eqn:F-sequence}
	F_{n} = \frac{F_{1}}{2} \left( \cos \left( \frac{n \pi}{2} \right) - 1 \right) ,
\end{equation}
and since both $C_{n}$ and $D_{n}$ need to satisfy the initial value of $0$, each of then is half of $F_{n}$,
\begin{equation} \label{eqn:C-D-sequences}
	C_{n} = D_{n} = \frac{F_{n}}{2} = \frac{F_{1}}{4} \left( \cos \left( \frac{n \pi}{2} \right) - 1 \right) .
\end{equation}
Next, by calculating the vacuum expectation value (VEV) of the commutator \eqref{eqn:L-commutator-2} with $|m| \neq |k|$ and $n = p = 1$, we find that $F_{1} = 0$, thus both sequences $C_{n} = D_{n} = 0$ vanish and we conclude that the quantum version of our algebra \emph{has no anomalies}. This is a relevant result, since it could mean our model doesn't need a specific number of dimensions to work, which will be explored again later in section \ref{sec:discussion}.

A quick calculation reveals that the WS Hamiltonian and momentum operators are given by
\begin{align}
	\Hat{H} & = - \frac{1}{2} \sum _{n} \Hat{\widetilde{L}}_{n , n} \label{eqn:WS-Hamiltonian}              \\
	\Hat{P} & = - \frac{1}{2} \sum _{n} \frac{n}{E_{n}} \Hat{\widetilde{L}}_{n , n} \label{eqn:WS-momentum}
\end{align}
since those generate $\tau$ and $\sigma$ translations respectively
\begin{align}
	\left[ \Hat{H} , \Hat{X}^{\mu} \right] & = - i \del _{\tau} \Hat{X}^{\mu} \label{eqn:tau-generator}     \\
	\left[ \Hat{P} , \Hat{X}^{\mu} \right] & = i \del _{\sigma} \Hat{X}^{\mu} . \label{eqn:sigma-generator}
\end{align}
Clearly, $\Hat{P}$ does not necessarily annihilate physical states (see \eqref{eqn:WS-momentum}), thus those are not required to be invariant under rigid rotations of the string. \emph{Physical states for the KG string have non-conserved WS momentum.} Also, we see that there is no level-matching between left and right-moving modes since those are not distinct in our model.

@@

@@

>>>>

When looking at the constraints, we see that we can't decouple the exponentials in $\tau$ from any of the sums, thus we get two-indices \textquotedblleft Virasoro modes"
\begin{subequations}
	\begin{align}
		L_{n , p} := \alpha ^{\mu} _{n} \alpha ^{\nu} _{p} \eta _{\mu \nu}                                                         & = 0 , \ \forall \ n , p \in \mathbb{Z} , \label{eqn:"virasoro"-modes-1} \\
		\widetilde{L}_{n , p} := \alpha ^{\mu} _{n} (\alpha ^{\nu} _{p})^{*} \eta _{\mu \nu}                                       & = 0 , \ n \neq p , \label{eqn:"virasoro"-modes-2}                       \\
		\sum _{n} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) & = 0 \label{eqn:"virasoro"-modes-sum} .
	\end{align}
\end{subequations}
Constraint \eqref{eqn:"virasoro"-modes-2} implies that we only have $D$ independent expansion modes for each field $X^{\mu}$, which for consistency as we will see later means $\alpha ^{\mu} _{- p} = \alpha ^{\mu} _{p} , \ p \leq d = D - 1$ and $\alpha ^{\mu} _{n} = 0 , \ \forall \ |n| > d$, so we have a truncated solution. This is not surprising, since because space-time is discrete we expect wavelengths smaller than the granular structure to be ruled out.

@@

We start by calculating the canonical momentum density conjugate to the fields $X^{\mu} (x)$, $\Pi ^{\nu} (x)$, given by
\begin{multline} \label{eqn:canonical-momentum-density}
	\Pi ^{\nu} (x) = F^{-} \frac{i}{8 \pi \alpha '} \sum _{n} \bigg( \alpha ^{\nu} _{n} \e ^{i (E_{n} \tau - n \sigma)} - \\
	- (\alpha ^{\nu} _{n})^{*} \e ^{- i (E_{n} \tau - n \sigma)} \bigg)
\end{multline}
where
\begin{multline} \label{eqn:F-minus-full-sum}
	F^{-} = 1 - \frac{k \Delta}{2 \e ^{2 \phi (x)}} = \\
	= \sum _{l} \left( A_{l} \e ^{i (E_{l} \tau + l \sigma)} + (A_{l})^{*} \e ^{- i (E_{l} \tau + l \sigma)} \right) ,
\end{multline}
and then proceed to use the equal-time Poisson bracket relation at $\tau = 0$
\begin{equation} \label{eqn:canonical-bracket-relation}
	\left\{ X^{\mu} (0 , \sigma) , \Pi ^{\nu} (0 , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
\end{equation}
to calculate the bracket relations between the expansion modes $\alpha ^{\mu} _{n}$ and $(\alpha ^{\nu} _{p})^{*}$. After using the freedom we still have in choosing the expansion modes of $F^{-}$ to gauge fix it to satisfy $\mathfrak{Re} (A_{0}) = - 2 \alpha '$ and realizing that $\alpha ^{\mu} _{- n} = \alpha ^{\mu} _{n}$, we get the desired
\begin{subequations}
	\begin{align}
		\left\{ \alpha ^{\mu} _{n} , \alpha ^{\nu} _{p} \right\}       & = 0 = \left\{ (\alpha ^{\mu} _{n})^{*} , (\alpha ^{\nu} _{p})^{*} \right\} \label{eqn:expansion-modes-bracket-0} \\
		\left\{ \alpha ^{\mu} _{n} , (\alpha ^{\nu} _{p})^{*} \right\} & = - i E_{n} \delta _{|n| , |p|} \eta ^{\mu \nu} , \label{eqn:expansion-modes-bracket-1}
	\end{align}
\end{subequations}
from which we can normalize the expansion modes to get harmonic oscillator modes and bracket relations
\begin{subequations}
	\begin{align}
		a^{\mu} _{n}       & := \frac{1}{\sqrt{E_{n}}} \alpha ^{\mu} _{n} \label{eqn:normalized-oscillator-modes}         \\
		(a^{\mu} _{n})^{*} & := \frac{1}{\sqrt{E_{n}}} (\alpha ^{\mu} _{n})^{*} \label{eqn:normalized-oscillator-modes-*}
	\end{align}
\end{subequations}
\begin{equation} \label{eqn:harmonic-bracket-relations}
	\left\{ a^{\mu} _{n} , (a^{\nu} _{p})^{*} \right\} = - i \delta _{|m| , |l|} \eta ^{\mu \nu} .
\end{equation}
The bracket relations for $\alpha ^{\mu} _{0}$ can be used to get the expected bracket relations between $x^{\mu}$ and $p^{\nu}$
\begin{align}
	\left\{ x^{\mu} , x^{\nu} \right\} & = 0 = \left\{ p^{\mu} , p^{\nu} \right\} \label{eqn:x-x-p-p-brackets} \\
	\left\{ x^{\mu} , p^{\nu} \right\} & = \eta ^{\mu \nu} . \label{eqn:x-p-bracket-relations}
\end{align}

@@

Having the bracket relations between the vibrational modes of the string, we can now calculate the constraint algebra, which we shall refer to as the Virasoro-Klein-Gordon Algebra. For simplicity, since $E_{n} = \sqrt{n^2 + \mu ^2} > 0$, we shall work with the normalized harmonic oscillator modes $a^{\mu} _{n}$ instead of the expansion modes $\alpha ^{\mu} _{n}$. The algebra is given by
\begin{subequations}
	\begin{equation} \label{eqn:L-brackets-0}
		\left\{ L_{n , m} , L_{k , p} \right\} = 0
	\end{equation}
	\begin{equation} \label{eqn:L-brackets-1}
		\left\{ L_{n , m} , \widetilde{L}_{k , p} \right\} = - i \left( L_{m , k} \delta _{|n| , |p|} + L_{n , k} \delta _{|m| , |p|} \right)
	\end{equation}
	\begin{equation} \label{eqn:L-brackets-2}
		\left\{ \widetilde{L}_{n , m} , \widetilde{L}_{k , p} \right\} = - i \left( \widetilde{L}_{k , m} \delta _{|n| , |p|} - \widetilde{L}_{n , p} \delta _{|m| , |k|} \right) .
	\end{equation}
\end{subequations}

@@

We now seek to quantize the Klein-Gordon string by means of covariant canonical quantization, in a manner much similar to those found in (\cite{Tong2009Lectures},\cite{Green2012Superstring}). The string coordinates $X^{\mu}$ and it's conjugate momentum $\Pi ^{\nu}$ are turned into operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$, with the Poisson brackets $\{ . , . \}$ being replaced by commutators $\{ . , . \} \rightarrow - i [ . , . ]$:
\begin{subequations}
	\begin{align}
		\left[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \right] & = i \delta (\sigma - \sigma ') \eta ^{\mu \nu} \label{eqn:X-P-commutator}                                              \\
		\left[ \Hat{X}^{\mu} , \Hat{X}^{\nu} \right]                                     & = 0 = \left[ \Hat{\Pi}^{\mu} , \Hat{\Pi}^{\nu} \right] \label{eqn:X-X-P-P-commutators}                                 \\
		\left[ \Hat{a}^{\mu} _{n} , \Hat{a}^{\nu} _{p} \right]                           & = 0 = \left[ (\Hat{a}^{\mu} _{n})^{\dagger} , (\Hat{a}^{\nu} _{p})^{\dagger} \right] \label{eqn:a-a-a*-a*-commutators} \\
		\left[ \Hat{a}^{\mu} _{n} , (\Hat{a}^{\nu} _{p})^{\dagger} \right]               & = \delta _{|n| , |p|} \eta ^{\mu \nu} \label{eqn:a-a*-commutator}                                                      \\
		\left[ \Hat{x}^{\mu} , \Hat{x}^{\nu} \right]                                     & = 0 = \left[ \Hat{p}^{\mu} , \Hat{p}^{\nu} \right] \label{eqn:x-x-p-p-commutators}                                     \\
		\left[ \Hat{x}^{\mu} , \Hat{p}^{\nu} \right]                                     & = i \eta ^{\mu \nu} \label{eqn:x-p-commutator}
	\end{align}
\end{subequations}

As usual, we define the vacuum state of the string to obey
\begin{equation} \label{eqn:annihilation-vacuum}
	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 .
\end{equation}
For $p = 0$ we have center of mass position and momentum, so the vacuum has extra structure obeying
\begin{subequations}
	\begin{align}
		\Hat{x}^{\mu} \ket{0 ; x} & = x^{\mu} \ket{0 ; x} \label{eqn:x-vacuum-x}                       \\
		\Hat{p}_{\mu} \ket{0 ; x} & = - i \frac{\del}{\del x^{\mu}} \ket{0 ; x} \label{eqn:p-vacuum-x}
	\end{align}
\end{subequations}
in position representation and
\begin{subequations}
	\begin{align}
		\Hat{x}^{\mu} \ket{0 ; p} & = - i \frac{\del}{\del p_{\mu}} \ket{0 ; p} \label{eqn:x-vacuum-p} \\
		\Hat{p}_{\mu} \ket{0 ; p} & = p_{\mu} \ket{0 ; p} \label{eqn:p-vacuum-p}
	\end{align}
\end{subequations}
in momentum representation.

@@

When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
\begin{subequations}
	\begin{equation} \label{eqn:L-constraint-quantum-1}
		\bra{\phi} \Hat{L}_{p , k} \ket{\psi} = 0 \, \,
	\end{equation}
	\begin{equation} \label{eqn:L-constraint-quantum-2}
		\bra{\phi} \Hat{\widetilde{L}}_{p , k} \ket{\psi} = 0 .
	\end{equation}
\end{subequations}
$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators. As for $\widetilde{L}_{p , k}$, we have an ambiguity for $p = k \neq 0$, so we pick normal ordering with the annihilation operator to the right
\begin{equation} \label{eqn:L-normal-ordering}
	\Hat{\widetilde{L}}_{p , p} = (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu} .
\end{equation}
This ambiguity manifests in the imposition of the constraint as
\begin{equation} \label{eqn:shifted-L-constraint}
	\bra{\phi} \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \Hat{\widetilde{L}}_{n , n} \right) - a \right) \ket{\psi} = 0 ,
\end{equation}
for some constant $a$. Classically, we had eq (\ref{eqn:string-rest-mass-classical-1}) for the string rest mass, from which we can now see that the string mass spectrum will get shifted by
\begin{multline} \label{eqn:shifted-mass-spectrum}
	\Hat{M}^2 = \frac{8}{\alpha '} \Bigg( \frac{2 \mu ^2}{\alpha '} \Hat{x}^{\mu} \Hat{x}_{\mu} - \\
	- \left( \sum _{n \neq 0} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} (\Hat{a}^{\mu} _{n})^{\dagger} \Hat{a}^{\nu} _{n} \eta _{\mu \nu} \right) - a \right) \Bigg) .
\end{multline}
This constant can be calculated by imposing normal-ordering on the summed constraint since $n \in (- d , d)$ is finite, and the result is
\begin{multline}
	a = - D \sum _{n \neq 0} \left( 1 + \frac{n}{E_{n}} \right) ^2 E_{n} = \\
	= - D \sum _{n > 0} \left( 1 + \frac{n^2}{E_{n} ^2} \right) E_{n} .
\end{multline}

The commutation relations between the constraints are inherited by the Poisson brackets
\begin{subequations}
	\begin{align}
		\left[ \Hat{L}_{n , m} , \Hat{L}_{k , p} \right]                         & = 0 \label{eqn:L-commutator-0}                                                                                                   \\
		\left[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right]             & = \Hat{L}_{m , k} \delta _{|n| , |p|} + \Hat{L}_{n , k} \delta _{|m| , |p|} \label{eqn:L-commutator-1}                           \\
		\left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] & = \Hat{\widetilde{L}}_{k , m} \delta _{|n| , |p|} - \Hat{\widetilde{L}}_{n , p} \delta _{|m| , |k|} \label{eqn:L-commutator-2} .
	\end{align}
\end{subequations}
The commutator (\ref{eqn:L-commutator-1}) ends up with only annihilation operators in the R.H.S, so it has no ordering ambiguities, meanwhile the commutator (\ref{eqn:L-commutator-2}) have ordering ambiguities for $|m| = |k|$ and/or $|n| = |p|$, so we add the anomalous terms
\begin{multline} \label{eqn:L-commutator-anomalous-initial}
	\left[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{k , p} \right] = \Hat{\widetilde{L}}_{k , m} \delta _{|n| , |p|} - \Hat{\widetilde{L}}_{n , p} \delta _{|m| , |k|} + \\
	+ C_{n} \delta _{|n| , |p|} + D_{k} \delta _{|m| , |k|} .
\end{multline}
Clearly, $C_{0} = D_{0} = 0$, since when all indices are $0$ we have only the position and momentum operators, and thus the commutator should vanish identically. Also, because of the symmetry in the indices we have that $C_{- n} = C_{n}$ and $D_{- k} = D_{k}$. Using the Jacobi identity we get the difference equation
\begin{equation} \label{eqn:F-difference-eqn}
	F_{n + 1} + F_{n} + F_{1} = 0
\end{equation}
for the sum of both sequences $F_{n} = C_{n} + D_{n}$. This difference equation has solution
\begin{equation} \label{eqn:F-sequence}
	F_{n} = \frac{F_{1}}{2} \left( \cos \left( \frac{n \pi}{2} \right) - 1 \right) ,
\end{equation}
and since both $C_{n}$ and $D_{n}$ need to satisfy the initial value of $0$, each of then is half of $F_{n}$,
\begin{equation} \label{eqn:C-D-sequences}
	C_{n} = D_{n} = \frac{F_{n}}{2} = \frac{F_{1}}{4} \left( \cos \left( \frac{n \pi}{2} \right) - 1 \right) .
\end{equation}
Next, by calculating the vacuum expectation value (VEV) of the commutator \eqref{eqn:L-commutator-2} with $|m| \neq |k|$ and $n = p = 1$, we find that $F_{1} = 0$, thus both sequences $C_{n} = D_{n} = 0$ vanish and we conclude that the quantum version of our algebra \emph{has no anomalies}. This is a relevant result, since it could mean our model doesn't need a specific number of dimensions to work, which will be explored again later in section \ref{sec:discussion}.

A quick calculation reveals that the WS Hamiltonian and momentum operators are given by
\begin{subequations}
	\begin{align}
		\Hat{H} & = - \frac{1}{2} \sum _{n} \Hat{\widetilde{L}}_{n , n} \label{eqn:WS-Hamiltonian}              \\
		\Hat{P} & = - \frac{1}{2} \sum _{n} \frac{n}{E_{n}} \Hat{\widetilde{L}}_{n , n} \label{eqn:WS-momentum}
	\end{align}
\end{subequations}
since those generate $\tau$ and $\sigma$ translations respectively
\begin{subequations}
	\begin{align}
		\left[ \Hat{H} , \Hat{X}^{\mu} \right] & = - i \del _{\tau} \Hat{X}^{\mu} \label{eqn:tau-generator}     \\
		\left[ \Hat{P} , \Hat{X}^{\mu} \right] & = i \del _{\sigma} \Hat{X}^{\mu} . \label{eqn:sigma-generator}
	\end{align}
\end{subequations}
Clearly, $\Hat{P}$ does not necessarily annihilate physical states (see \eqref{eqn:WS-momentum}), thus those are not required to be invariant under rigid rotations of the string. \emph{Physical states for the KG string have non-conserved WS momentum.} Also, we see that there is no level-matching between left and right-moving modes since those are not distinct in our model.

@@

\begin{subequations}

@@

\end{subequations}
